Examining a Quarter Century of Publishing Trends in Social Work Research:

### 2015-04-17 manuscript.Rmd
Updated plots.

```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")

@@

plot.article.count <- ggplot(nsf, aes(as.factor(years), 
    y = n.grads, group=1)) + 
    geom_line(colour="red") + 
    geom_point(colour="red") + 
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    ggtitle("A. Number of Articles by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    ylim(c(0,2200)) + 
    geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
    geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") 
```

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
    ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
    annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
    ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")  
```

@@

plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
    geom_line(size = .75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year")
```

@@

page.plot <- ggplot(pages.df.melted, aes(years, value, group = 
    variable, color=variable)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,16)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Article Length by Year")
```

```{r nsfPlot, eval=TRUE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
    scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
    ylab("Doctoral degrees") +
    xlab("Year") +
    geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10)) +
    ggtitle("Number of Earned Social Work Doctoral Degrees by Year") 
```

>>>>

```{r imageMaker, comment=NA, echo=FALSE, eval=TRUE}
# Read data files
options(stringsAsFactors = FALSE)
load("/Users/beperron/Git/SocialWorkResearch/Data/ebscoFULL.R")
load("/Users/beperron/Git/SocialWorkResearch/Data/proQuest.R")
hodge <- readLines("/Users/beperron/Git/SocialWorkResearch/search_specifications/hodge.txt", n = -1)
hIndex <- read.csv("/Users/beperron/Git/SocialWorkResearch/Data/hIndex.csv")
hIndex$h5Index <- ifelse(is.na(hIndex$h5Index), 0, hIndex$h5Index)
hIndex$h5Median <- ifelse(is.na(hIndex$h5Median), 0, hIndex$h5Median)

@@

#Annotation data file
articles.x <- as.factor(articles.year.df[c(1, 6, 12, 18, 25), 1]) 
articles.y <- articles.year.df[c(1, 6, 12, 18, 25), 2] 
articles.label <- as.character(articles.y)
articles.placement <- articles.y-50

articles.x1 <- as.factor(ar)

plot.article.count <- ggplot(nsf, aes(as.factor(years), 
    y = n.grads, group=1)) + 
    geom_line(colour="red") + 
    geom_point(colour="red") + 
    #geom_point(colour="red") + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Articles") + 
    ggtitle("A. Number of Articles by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    ylim(c(0,2200)) + 
    geom_line(data = articles.year.df, aes(as.factor(years), y = year.count), colour="steelblue") + 
    #geom_text(data = nsf, aes(label = n.grads), vjust = 2, size = 2.75) +
    geom_point(data = articles.year.df, aes(as.factor(years), y = articles.year.df$year.count), colour="steelblue") + 
    annotate("text", factor(c(2002, 2005, 2008, 2012)), 
    c(165, 225, 250, 190) + 150, label = c("238","323", "338", "280") , size = 3) + 
    annotate("text", articles.x, articles.placement, label = articles.label, size=3) + 
    annotate("point", x = as.factor(2003), y = 720, alpha = .60, color = "green", size = 6) + 
    annotate("point", x = as.factor(2015), y = 750, alpha = .60, color = "green", size = 6)

@@

plot.journal.count <- ggplot(n.journals.year, aes(as.factor(record.y), 
    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) +
    annotate("rect", xmin = 2008-1989+1, xmax =  2012-1989+1, 
    ymin = 55, ymax = 70, alpha = .20, fill= "#0072B2") +
    annotate("rect", xmin = 2005-1989+1, xmax =  2007-1989+1, 
    ymin = 53, ymax = 62, alpha = .20, fill = "#0072B2")

plot.journal.count2 <- ggplot(n.journals.year, aes(as.factor(record.y), 
    y = Journal.count, group=1)) + 
    geom_line(colour="black") +
    theme(axis.text.x = element_text(angle = 45, hjust = 1, size=8), 
    title = element_text(size = 10), plot.title=element_text(size=10)) + 
    xlab("Year") + 
    ylab("Journals") + 
    ggtitle("B. Number of Journals by Year") +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(breaks = c(seq(0, 100, 10)), limits = c(20, 70)) 
```

@@

n_authors2$ymin <- n_authors2$Average - n_authors2$Standard_Deviation
n_authors2$ymax <- n_authors2$Average - n_authors2$Standard_Deviation

plot.author.count2 <- ggplot(n_authors2, aes(ID, y = Average, group=1, size = Standard_Deviation, colour=as.factor(Median))) + 
    geom_line(size=.75) +
    geom_point() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year")

plot.author.count <- ggplot(n_authors2_melted, aes(x = pubYear, y = value, group = summaryStat, colour = summaryStat)) + 
    geom_line(size = .75) + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,2.5)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Authors Per Article by Year")

@@

page.plot <- ggplot(pages.df.melted, aes(years, value, group = 
    variable, color=variable)) + 
    geom_line() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_colour_manual(values=cbPalette)  +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(0,16)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Article Length by Year")

page.plot <- ggplot(pages.df, aes(years, Mean.Pages, colour=as.factor(Median.Pages), size = Std.Pages, group = 1))+ 
    geom_line(size=.75) +
    geom_point() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    title = element_text(size = 10), 
    legend.title=element_blank()) +
    scale_x_discrete(breaks=c(seq(1989, 2013, 2))) +
    scale_y_continuous(limits = c(10.5,16)) +
    ylab("Value") +
    xlab("Year") +
    ggtitle("Article Length by Year")
````

```{r nsfPlot, eval=TRUE}
plot.PhD <- ggplot(nsf, aes(years, n.grads, group=1)) + 
    geom_line(linetype="dotted", colour = "#0072B2", size = .75) + 
    geom_point(colour = "#0072B2", size = .75) +
    scale_y_continuous(breaks = c(seq(0, 350, 25)), limits = c(200,350)) +
    ylab("Doctoral degrees") +
    xlab("Year") +
    #geom_text(aes(label = n.grads), vjust = -1.2, size = 2.75) + 
    #theme(axis.text.x = element_text(angle = 45, hjust = 1), 
    #title = element_text(size = 10)) +
    #ggtitle("Number of Earned Social Work Doctoral Degrees by Year")
    geom_text(aes(2002, 230, label = "238", colour = "black"))
```
